---
name: Taylor Winter
position: "PhD Candidate"
#address: "203/42 Constable Street, Newtown, Wellington"
phone: +64 22 171 1260
email: "taylor.winter@vuw.ac.nz"
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)

Sys.getenv("ORCID_TOKEN")
```

# Summary

I am currently studying a PhD at the University of Victoria Wellington. My research is in health psychology, focusing on how mood can be influenced by physiological and environmental factors such as the gut-microbiome and experiences of discrimination. Work has led to a broad range of experience in statistical methods including structural equation modelling, multi-level modelling, and Bayesian methods. In particular, this experience has led to a tutorial article on informed Bayesian analysis, and the development of statistical software to make complex techniques more accesible.

I also work with Stats NZ and Ngāi Tahu providing statistical advice and conducting analytics. I have extensive experience working on a range of survey and administrative datasets, mainly using a large data warehouse of Government data called the Integrated Data Infrastructure (IDI). My background is in Bayesian modelling and big data. I have worked on a range of projects including the development of official statistics for government and pipeline development for cellphone data from Spark and Vodafone.

# Employment

```{r employment}
work <- rorcid::orcid_employments("0000-0001-5097-9163")

work$`0000-0001-5097-9163`$`employment-summary` %>%
  detailed_entries(
    what = `role-title`,
    where = ifelse(is.na(`end-date.year.value`),
                  glue::glue("{`start-date.year.value`} - Present"),
                  glue::glue("{`start-date.year.value`} - {`end-date.year.value`}")
                  ),
    with = organization.name,
    #where = organization.address.city
  )
```
 
# Education

```{r education}
edu <- rorcid::orcid_educations("0000-0001-5097-9163")

edu$`0000-0001-5097-9163`$`education-summary` %>% 
  detailed_entries(
    what = `role-title`, 
    when = ifelse(is.na(`end-date.year.value`),
                  "Present",
                  glue::glue("{`end-date.year.value`}")
                  ),
    with = organization.name,
    where = organization.address.city
  )
```

# Awards and scholarships

```{r awards}
tribble(
  ~award, ~from, ~year,
  "IPANZ Young Professional Of The Year (Top 3)", "Institute of Public Administration NZ", "2018",
  "Victoria Doctoral Scholarship (Differed)", "Victoria University of Wellington", "2018",
  "Otago Research Master's Scholarship", "University of Otago", "2015"
) %>%
  brief_entries(award, year, from)
```

# Publications

```{r publications}
bibliography_entries("../pubs.bib")

```

# Presentations and posters

```{r presentations}
tribble(
  ~who, ~date, ~where,
  "Using overseas surveys to produce reliable models of sexual minorities", "2019", "New Zealand Population Conference, Wellington",
  "Alcohol use disparities among gender and sexual minorities in New Zealand (Poster)", "2019", "Collaborative Perspectives on Addiction, Rhode Island",
  "Iwi data tool using integrated data and R Shiny", "2017", "Iwi Data Conference, Christchurch",
  "Using data to support a collective impact model of Māori potential", "2016", "Population Association of New Zealand Conference, Christchurch",
  "The effect of motherhood on income", "2016", "New Zealand Association of Economists conference, Wellington",
  "A machine learning approach to classifying life course outcomes", "2016", "Longitudinal and multivariate analysis network (Stats NZ), Wellington",
  "Methodology for comparing incomes between parents and non-parents", "2016", "Statistical methods seiminar (Stats NZ), Wellington",
  "Inter-hemispheric inhibition in the autistic brain", "2014", "Neuroethics seminar, Dunedin"
) %>%
  detailed_entries(with = who, what = where, where = date)
```

# Skills

* Languages such as SQL, R, Python, SAS, SPSS Syntax, Bash
* Structural equation modelling and causal analysis
* Bayesian statistics, using _brms_ in R (Stan backend)
* Machine learning techniques such as random forests and neural nets
* Strong background using big data, i.e. the Integrated Data Infrastructure (IDI) at Stats NZ
* Knowledge of Tikanga Māori