---
name: Taylor Winter
position: "PhD Candidate"
#address: "203/42 Constable Street, Newtown, Wellington"
phone: +64 22 171 1260
email: "taylor.winter@vuw.ac.nz"
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)

```

# Summary

I am currently studying my PhD at the University of Victoria, Wellington while also working as a Senior Data Scientist at New Zealand's national statistics agency (Statistics NZ). My main line of research in my PhD investigates changes in authoritarian under varying levels of threat due to COVID-19. Through my research and current work commitments, I have a broad range of experience in statistical methods including structural equation modeling, multi-level modeling, and Bayesian methods.

# Employment

```{r employment}
work <- do.call("bind_rows",
  rorcid::orcid_employments("0000-0001-5097-9163")$`0000-0001-5097-9163`$`affiliation-group`$summaries
) %>%
  rename_all(function(x){gsub("employment-summary.", "", x)})

work %>%
  detailed_entries(
    what = `role-title`,
    where = ifelse(is.na(`end-date.year.value`),
                  glue::glue("{`start-date.year.value`} - Present"),
                  glue::glue("{`start-date.year.value`} - {`end-date.year.value`}")
                  ),
    with = organization.name,
    #where = organization.address.city
  )
```
 
# Education

```{r education}

edu <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0001-5097-9163")$`0000-0001-5097-9163`$`affiliation-group`$summaries
) %>%
  rename_all(function(x){gsub("education-summary.", "", x)})

edu %>% 
  detailed_entries(
    what = `role-title`, 
    when = ifelse(is.na(`end-date.year.value`),
                  "Present",
                  glue::glue("{`end-date.year.value`}")
                  ),
    with = organization.name,
    where = organization.address.city
  )
```

# Awards and scholarships

```{r awards}
tribble(
  ~award, ~with, ~year,
  "IPANZ Young Professional Of The Year (Top 3)", "Institute of Public Administration NZ", "2018",
  "Victoria Doctoral Scholarship", "Victoria University of Wellington", "2018",
  "Otago Research Master's Scholarship", "University of Otago", "2015"
) %>%
  brief_entries(what=award, when=year, with=with)
```

# Publications

```{r publications}
bibliography_entries("../pubs.bib")

```

# Presentations and posters

```{r presentations}
tribble(
  ~who, ~date, ~where,
  "Authoritarian submission on the left and right during the covid-19 pandemic in New Zealand", "2020", "New Zealand Psychological Society Conference, Wellington",
  "Using overseas surveys to produce reliable models of sexual minorities", "2019", "New Zealand Population Conference, Wellington",
  "Alcohol use disparities among gender and sexual minorities in New Zealand (Poster)", "2019", "Collaborative Perspectives on Addiction, Rhode Island",
  "Iwi data tool using integrated data and R Shiny", "2017", "Iwi Data Conference, Christchurch",
  "Using data to support a collective impact model of Māori potential", "2016", "Population Association of New Zealand Conference, Christchurch",
  "The effect of motherhood on income", "2016", "New Zealand Association of Economists conference, Wellington",
  "A machine learning approach to classifying life course outcomes", "2016", "Longitudinal and multivariate analysis network (Stats NZ), Wellington",
  "Methodology for comparing incomes between parents and non-parents", "2016", "Statistical methods seiminar (Stats NZ), Wellington",
  "Inter-hemispheric inhibition in the autistic brain", "2014", "Neuroethics seminar, Dunedin"
) %>%
  detailed_entries(with = who, what = where, where = date)
```

# Skills

* Health psychology research
* Social psychology research
* Research design and analysis
* Structural equation modelling and causal analysis
* Bayesian statistics and multi-level modelling
* Machine learning techniques such as random forests and neural nets
* Teaching reproducible research practices and statistics
* Knowledge of Tikanga Māori