---
name: Taylor Winter
position: "PhD Candidate"
#address: "203/42 Constable Street, Newtown, Wellington"
phone: +64 22 171 1260
email: "taylor.winter@vuw.ac.nz"
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)

```

# Summary

I am currently studying a PhD at the University of Victoria, Wellington while also working as a statistician at Statistics New Zealand. My core research is in social psychology, focusing on authoritarianism . Work has led to a broad range of experience in statistical methods including structural equation modelling, multi-level modelling, and Bayesian methods. As part of my study, I also share my statistical knowledge via means such as a tutorial article on informed Bayesian analysis, and the development of statistical software to make complex techniques more accesible.

I also work with Stats NZ and Ngāi Tahu providing statistical advice and conducting analytics. My specialty is Bayesian modelling and big data. This has led to me developing skill in reproducible workflows and project management techniques which I can bring to an academic role. Example projects include heading the development of an official statistic on poverty and pipeline development for cellphone data from Spark and Vodafone.

# Employment

```{r employment}
work <- do.call("bind_rows",
  rorcid::orcid_employments("0000-0001-5097-9163")$`0000-0001-5097-9163`$`affiliation-group`$summaries
) %>%
  rename_all(function(x){gsub("employment-summary.", "", x)})

work %>%
  detailed_entries(
    what = `role-title`,
    where = ifelse(is.na(`end-date.year.value`),
                  glue::glue("{`start-date.year.value`} - Present"),
                  glue::glue("{`start-date.year.value`} - {`end-date.year.value`}")
                  ),
    with = organization.name,
    #where = organization.address.city
  )
```
 
# Education

```{r education}

edu <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0001-5097-9163")$`0000-0001-5097-9163`$`affiliation-group`$summaries
) %>%
  rename_all(function(x){gsub("education-summary.", "", x)})

edu %>% 
  detailed_entries(
    what = `role-title`, 
    when = ifelse(is.na(`end-date.year.value`),
                  "Present",
                  glue::glue("{`end-date.year.value`}")
                  ),
    with = organization.name,
    where = organization.address.city
  )
```

# Awards and scholarships

```{r awards}
tribble(
  ~award, ~with, ~year,
  "IPANZ Young Professional Of The Year (Top 3)", "Institute of Public Administration NZ", "2018",
  "Victoria Doctoral Scholarship", "Victoria University of Wellington", "2018",
  "Otago Research Master's Scholarship", "University of Otago", "2015"
) %>%
  brief_entries(what=award, when=year, with=with)
```

# Publications

```{r publications}
bibliography_entries("../pubs.bib")

```

# Presentations and posters

```{r presentations}
tribble(
  ~who, ~date, ~where,
  "Authoritarian submission on the left and right during the covid-19 pandemic in New Zealand", "2020", "New Zealand Psychological Society Conference, Wellington",
  "Using overseas surveys to produce reliable models of sexual minorities", "2019", "New Zealand Population Conference, Wellington",
  "Alcohol use disparities among gender and sexual minorities in New Zealand (Poster)", "2019", "Collaborative Perspectives on Addiction, Rhode Island",
  "Iwi data tool using integrated data and R Shiny", "2017", "Iwi Data Conference, Christchurch",
  "Using data to support a collective impact model of Māori potential", "2016", "Population Association of New Zealand Conference, Christchurch",
  "The effect of motherhood on income", "2016", "New Zealand Association of Economists conference, Wellington",
  "A machine learning approach to classifying life course outcomes", "2016", "Longitudinal and multivariate analysis network (Stats NZ), Wellington",
  "Methodology for comparing incomes between parents and non-parents", "2016", "Statistical methods seiminar (Stats NZ), Wellington",
  "Inter-hemispheric inhibition in the autistic brain", "2014", "Neuroethics seminar, Dunedin"
) %>%
  detailed_entries(with = who, what = where, where = date)
```

# Skills

* Health psychology research
* Research design and analysis
* Structural equation modelling and causal analysis
* Bayesian statistics and multi-level modelling
* Machine learning techniques such as random forests and neural nets
* Teaching reproducible research practices and statistics
* Knowledge of Tikanga Māori